Reproducible Plant Pathology

### 2017-07-05 README.rmd
Update README file with more information about project

- the manuscript as submitted (in MS Word format) and its `Rmd` source file (in the `paper/` directory)  
- supplementary information source files (in `Rmd` format) and executed versions  
- all the figures that are included in the paper (in the `figures/` directory)

@@

We used [RStudio](http://www.rstudio.com/products/rstudio/) on MacOS and Ubuntu 16.04 LTS.

>>>>

- the manuscript as submitted (in MS Word format) and its `Rmd` source file (in
the `paper/` directory)

- supplementary information source files (in `Rmd` format) and executed versions

- all the figures that are included in the paper (in the `figures/` directory)

### The external files

Much of the collaborative work was done outside of GitHub and R using Google
Sheets. You can view the [article notes](https://drive.google.com/open?id=19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M) that we collected in the "article_evaluations" tab. Where "template" and
"article_notes" are used in creating that tab and are explained the "Assigning
Articles" vignette of this R package.

@@

We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
16.04 LTS.

We also used [JabRef](http://www.jabref.org/) and [Google Sheets](https://www.google.com/sheets/about/).
